---
title: "DMR comparison"
output: pdf_document
---

<!-- Created by Daniel Beck on 7/14/2015 -->
<!-- Modified: -->
<!--      7/21/2015 Continued development. Tested on Finch datasets. -->

<!-- This script compares two (or more?) lists of DMR (or more generally, chromosome regions) and generates potentially useful figures and tables. -->


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(pander)
library(GenomicRanges)
library(VennDiagram)
source("customFunctions.R")

# define datasets to compare
analysis<-c("sperm2_1e-4","sperm2_5e-2_fdr","sperm3_1e-3", "rbc2_1e-4","rbc2_5e-2_fdr", "rbc3_1e-3")
resultsFiles<-c(
     "/projects/steelheadSperm/results/all/",
     "/projects/steelheadSperm/results/all/",
     "/projects/steelheadSperm/results/all/",
     "/projects/steelheadRBC/results/all/",
     "/projects/steelheadRBC/results/all/",
     "/projects/steelheadRBC/results/all/"
)
dataNamesFiles<-c(
     "/projects/steelheadSperm/code/dataNames.R",
     "/projects/steelheadSperm/code/dataNames.R",
     "/projects/steelheadSperm/code/dataNames.R",
     "/projects/steelheadRBC/code/dataNames.R",
     "/projects/steelheadRBC/code/dataNames.R",
     "/projects/steelheadRBC/code/dataNames.R"
)


# define p-values to use
selectedPvalues<-c(1e-4, 0.05, 1e-3, 1e-4, 0.05, 1e-3)
# can be allWindow, twoWindow, threeWindow, MTCallWindow, MTCtwoWindow, MTCthreeWindow
pValueType<-c("twoWindow", "MTCtwoWindow", "threeWindow", "twoWindow", "MTCtwoWindow", "threeWindow")

resultsList<-list()
dmrNumberList<-list()
for (i in 1:length(analysis)){
     # load results into temporary environment
     dnTemp<-new.env()
     source(dataNamesFiles[[i]], local=dnTemp)
     temp = local({load(paste(resultsFiles[[i]], "methLists.RData", sep="")); environment()})
     dmrNumberList[[i]]<-temp$dmrNumberTable
     # find correct p-value
     spv<-which(dnTemp$pValues==selectedPvalues[[i]])
     # extract selected DMR list
     if (pValueType[i]=="allWindow"){
          resultsList[[i]]<-temp$methList[[spv]]
     } else if (pValueType[i]=="twoWindow"){
          resultsList[[i]]<-temp$methList2p[[spv]]
     } else if (pValueType[i]=="MTCallWindow"){
          resultsList[[i]]<-temp$MTCmethList[[spv]]
     } else if (pValueType[i]=="MTCtwoWindow"){
          resultsList[[i]]<-temp$MTCmethList2p[[spv]]
     } else {
          warning("Invalid pValueType")
     }
     rm(temp)
}

# make sure chromosome start and stop are numeric
resultsList<-lapply(resultsList, function(i){
     i$start<-as.numeric(i$start)
     i$stop<-as.numeric(i$stop)
     i
})
# convert resultsList DMR tables to GRanges objects
gresultsList<-lapply(resultsList, makeGRangesFromDataFrame)

```

# Comparison information (`r format(Sys.Date(), format="%B %d %Y")`)
This report compares the `r paste(comparisonNames, collapse=", ")` datasets. 

### Number of DMRs at different edgeR p-value thresholds
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
#     matrix(unlist(lapply(dmrNumberList, function(i) i[,3])), ncol=length(dmrNumberList))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
# " "=LETTERS[1:length(comparisonNames)], 
summaryTable<-cbind("analysis"=comparisonNames, "p-value type"= pValueType, "p-value"=selectedPvalues, "DMR Number"=sapply(resultsList, nrow))
summaryTable<-as.data.frame(summaryTable)
pandoc.table(summaryTable, split.tables=Inf, style="rmarkdown", caption='This table shows the p-values and total DMR numbers for each analysis.')
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# nameLabels<-paste(LETTERS[1:length(comparisonNames)], sapply(resultsList, nrow), sep=":")
# if (length(comparisonNames)==4){
#      silent<-vennCustomFour(a=gresultsList[[1]], b=gresultsList[[2]], c=gresultsList[[3]], d=gresultsList[[4]], names=nameLabels)
# } else if (length(comparisonNames)==3){
#      silent<-vennCustomThree(a=gresultsList[[1]], b=gresultsList[[2]], c=gresultsList[[3]], names=nameLabels)
# } else if (length(comparisonNames)==2){
#      silent<-vennCustomTwo(a=gresultsList[[1]], b=gresultsList[[2]], names=nameLabels)
# } else {
#      warning("No valid comparison")
# }
vennBarSet(gdmrList=gresultsList, names=comparisonNames, col=c("blue", "red"), scale=TRUE)

```

**Figure 1.** This figure shows the number of overlapping DMRs in the different analyses. All pairwise comparisons are shown. The blue bars show the number of DMRs unique to the first analysis The red bars show the number of DMRs unique to the second analysis Purple areas show the number of simple overlaps between the two analyses. Complex overlaps (involving multiple DMRs in one analysis) are shown in intermediate colors.

